Component response rate variation drives stability in large complex systems

### 2018-06-05 notebook/SI.Rmd
Semi-colon
Add in the text of Issue #1 to remind myself to write and include further detail on the matsh of gamma in future SI versoins

```{r, eval = FALSE}
install_github("bradduthie/RandomMatrixStability")
```

@@

>>>>

```{r, eval = FALSE}
install_github("bradduthie/RandomMatrixStability");
```

@@

<!---

Further explanation of $\gamma$ {#moregamma}

It would be perhaps useful to include a more detailed explanation of what $\gamma$ does in the context of the $M$. That is, as in @patel2018, I'm looking at $\frac{d N_{i}}{dt}$ and $\frac{d N_{j}}{dt}$, with $N_{i}$ and $N_{j}$ potentially affecting one another -- the $\gamma$ parameter modulates the change in each with respect to time at local equilibrium; in the language of @patel2018, it "determines the timescale separation" between the dynamics of individual components in the system $M$. The best place to provide further detail for this is likely to be early on in the Supplemental Information.

--->
